% ******************************* Thesis Declaration ***************************

\begin{declaration}

I hereby declare that the contents presented in this dissertation are original and have been carried out by myself under the guidance of my supervisor Prof. Bruno Clerckx.
Any work from other researchers, scholars, or sources have been properly cited and acknowledged.
The contents have not been submitted in whole or in part for consideration of any other degree or qualification in any academic institution.
I am aware of the ethical standards and academic integrity policies of Imperial College London, and I have adhered to these principles throughout the course of my study.
In signing this declaration, I affirm my commitment to academic honesty, intellectual integrity, and the pursuit of knowledge in the service of truth and understanding.

The copyright of this thesis rests with the author. Unless otherwise indicated, its contents are licensed under a \href{https://creativecommons.org/licenses/by-nc/4.0/deed.en}{Creative Commons Attribution-Non Commercial 4.0 International License} (CC BY-NC). Under this license, you may copy and redistribute the material in any medium or format. You may also create and distribute modified versions of the work. This is on the condition that: you credit the author and do not use it, or any derivative works, for a commercial purpose. When reusing or sharing this work, ensure you make the license terms clear to others by naming the license and linking to the license text. Where a work has been adapted, you should indicate that the work has been changed and describe those changes. Please seek permission from the copyright holder for uses of this work that are not included in this license or permitted under UK Copyright Law.

The source code of all simulation results in this dissertation are publicly available at \url{https://github.com/snowztail/}.

\end{declaration}
